Evaluating the Effectiveness of Statistical Models in Analyzing Mortality in Canada

### 2024-03-17 outputs/paper.Rmd
1

```{r echo = FALSE}
#| label: tbl-1
#| tbl-cap: "Modeling the most prevalent cause of deaths in Canada, 2000-2022"
cleaned_data <- read.csv("cleaned_data")
cleaned_data <- cleaned_data[, -1]

>>>>

```{r echo = FALSE}
#| label: tbl-1
#| tbl-cap: "Modeling the most prevalent cause of deaths in Canada, 2000-2022"
cleaned_data <- read.csv(here::here("cleaned_data"))
cleaned_data <- cleaned_data[, -1]

### 2024-03-17 outputs/paper.qmd
1

### Preview
```{r echo = FALSE}
#| label: tbl-1
#| tbl-cap: "Modeling the most prevalent cause of deaths in Canada, 2000-2022"
cleaned_data <- read.csv("cleaned_data")
cleaned_data <- cleaned_data[, -1]

>>>>

### Preview
```{r echo = FALSE}
#| label: tbl-1
#| tbl-cap: "Modeling the most prevalent cause of deaths in Canada, 2000-2022"
cleaned_data <- read.csv(here::here("inputs/cleaned_data"))
cleaned_data <- cleaned_data[, -1]
